\documentclass{article}
\usepackage[utf8]{inputenc}

\title{Responses for the Reading Questions 1: What is Linear Algebra?}
\author{Yong Hoon, Do}
\date{\today}

\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{systeme}

\begin{document}

\maketitle

%--------------------------------------------------------------------------------

\section{Is the equation $x^2+xy+tan(y^3)=0$ linear or not? Why or why not?}

The given equation is not linear because the equation is neither a straight line nor a flat plane. According to the textbook, linear equations have to geometrically give a straight line or, a flat plane depending on the number of variables; every coefficients in equations must be a constant number. The coefficients of those given equations however, consist of compound variables with another variables. This fact leads the conclusion that the given equations are nonlinear equations.

%--------------------------------------------------------------------------------

\section{Find all solutions to the system of two linear equations 2x+3y=-8, x-y=6}

Now we have two equations

\[
\systeme{
  2x+3y=-8,
  x-y=6
}
\]

\bigskip

Solving simultaneous equations would work for this case, but eliminating one of the unknown value by substituting works too. We choose one of the equation and to find $x$~, we let $x-y=6$~ be
\begin{equation}
y=x-6
\end{equation}

Then substituting $y=x-6$ into the first equation $2x+3y=-8$
\begin{equation}
2x+3(x-6)=-8
\end{equation}

By using the distributive law and Commutative Laws
\begin{equation}
2x+3x=-8+18
\end{equation}

Thus, we end up with having the constant value for $x$,
\begin{equation}
x=2
\end{equation}

Substituting $x=2$ back to the original equation $x-y=6$~ and we have
\begin{equation}
2-y=6
\end{equation}

So that we get
\begin{equation}
y=-4
\end{equation}

For the conclusion, the only solution to this system of two linear equations is $(x,y)=(2,-4)$.



%--------------------------------------------------------------------------------

\section{Describe how the production manager might explain the importance of the procedures described in the trail mix application}

With the limited storage space, the production manager is able to maximize the profit as estimating the amounts of trail mix and resulting in minimizing any ingredients leftover each day.

\end{document}
